---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readxl)
library(janitor)
library(tidyverse)
```


```{r}
sides <- read_csv("clean_data/sides_clean.csv")
```


# Normalised macros for 100g are the same for some items that come in 2 portion sizes so one of them will be removed

```{r}
sides_100g <- sides %>%
  filter(type == "side") %>%
  filter(dish != "Chicken Kickers (14)" & dish != "Chicken Strippers (14)" &
           dish != "Chicken Wings (14)" & dish != "Pop'n Chicken Double Portion" &
           dish != "Potato Wedges IRL") 
```

```{r}
dips_100g <- sides %>%
  filter(type == "dip") %>%
  filter(dish != "BBQ Dip 100g" & dish != "Frank's Hot Dip 100g" &
           dish != "Garlic and Herb Dip 100g")
```



# SIDES

### kcal per 100g for sides

```{r}
kcal_sides <- sides_100g %>%
  select(dish, energy_kcal_100g) %>%
  group_by(dish) %>%
  summarise(energy_kcal = energy_kcal_100g)
kcal_sides
```


```{r}
kcal_sides %>%
  ggplot() +
  aes(reorder(x = dish, energy_kcal), y = energy_kcal) +
  coord_flip() +
  geom_col(fill = "darkblue")
```

### Fat per 100g for sides

```{r}
fat_sides <- sides_100g %>%
  select(dish, fat_g_100g) %>%
  group_by(dish) %>%
  summarise(fat = fat_g_100g)
fat_sides
```

```{r}
fat_sides %>%
  ggplot() +
  aes(reorder(x = dish, fat), y = fat) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### saturated per 100g for sides

```{r}
sat_sides <- sides_100g %>%
  select(dish, sat_g_100g) %>%
  group_by(dish) %>%
  summarise(sat = sat_g_100g)
sat_sides
```

```{r}
sat_sides %>%
  ggplot() +
  aes(reorder(x = dish, sat), y = sat) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### carbs per 100g of sides

```{r}
carb_sides <- sides_100g %>%
  select(dish, carb_g_100g) %>%
  group_by(dish) %>%
  summarise(carbs = carb_g_100g)
carb_sides
```


```{r}
carb_sides %>%
  ggplot() +
  aes(reorder(x = dish, carbs), y = carbs) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### sugars per 100g for sides

```{r}
sugar_sides <- sides_100g %>%
  select(dish, sugars_g_100g) %>%
  group_by(dish) %>%
  summarise(sugar = sugars_g_100g)
sugar_sides
```

```{r}
sugar_sides %>%
  ggplot() +
  aes(reorder(x = dish, sugar), y = sugar) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### fibre per 100g for sides

```{r}
fibre_sides <- sides_100g %>%
  select(dish, fibre_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = fibre_g_100g)
fibre_sides
```

```{r}
fibre_sides %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### protein per 100g for sides

```{r}
protein_sides <- sides_100g %>%
  select(dish, protein_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = protein_g_100g)
protein_sides
```


```{r}
protein_sides %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### salt per 100g for sides

```{r}
salt_sides <- sides_100g %>%
  select(dish, salt_g_100g) %>%
  group_by(dish) %>%
  summarise(salt = salt_g_100g)
salt_sides
```


```{r}
salt_sides %>%
  ggplot() +
  aes(reorder(x = dish, salt), y = salt) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### sodium per 100g for sides

```{r}
sodium_sides <- sides_100g %>%
  select(dish, sodium_g_100g) %>%
  group_by(dish) %>%
  summarise(sodium = sodium_g_100g)
sodium_sides
```


```{r}
sodium_sides %>%
  ggplot() +
  aes(reorder(x = dish, sodium), y = sodium) +
  coord_flip() +
  geom_col(fill = "darkblue")
```



### %RDA kcal for sides

```{r}
kcal_rda_sides <- sides_100g %>%
  select(dish, energy_kcal_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = energy_kcal_rda)
kcal_rda_sides
```


```{r}
kcal_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA fat for sides

```{r}
fat_rda_sides <- sides_100g %>%
  select(dish, fat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fat_rda)
fat_rda_sides
```


```{r}
fat_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA saturated for sides

```{r}
sat_rda_sides <- sides_100g %>%
  select(dish, sat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sat_rda)
sat_rda_sides
```

```{r}
sat_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of carbs for sides

```{r}
carb_rda_sides <- sides_100g %>%
  select(dish, carb_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = carb_rda)
carb_rda_sides
```

```{r}
carb_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA sugars for sides

```{r}
sugar_rda_sides <- sides_100g %>%
  select(dish, sugars_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sugars_rda)
sugar_rda_sides
```

```{r}
sugar_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA fibre of sides

```{r}
fibre_rda_sides <- sides_100g %>%
  select(dish, fibre_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fibre_rda)
fibre_rda_sides
```

```{r}
fibre_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA protein for sides

```{r}
protein_rda_sides <- sides_100g %>%
  select(dish, protein_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = protein_rda)
protein_rda_sides
```


```{r}
protein_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")

```


### %RDA salt for sides

```{r}
salt_rda_sides <- sides_100g %>%
  select(dish, salt_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = salt_rda)
salt_rda_sides
```


```{r}
salt_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA sodium for sides

```{r}
sodium_rda_sides <- sides_100g %>%
  select(dish, sodium_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sodium_rda)
sodium_rda_sides
```


```{r}
sodium_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


# DIPS

### kcal per 100g for dips

```{r}
kcal_dips <- dips_100g %>%
  select(dish, energy_kcal_100g) %>%
  group_by(dish) %>%
  summarise(energy_kcal = energy_kcal_100g)
kcal_dips
```


```{r}
kcal_dips %>%
  ggplot() +
  aes(reorder(x = dish, energy_kcal), y = energy_kcal) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### fat per 100g for dips

```{r}
fat_dips <- dips_100g %>%
  select(dish, fat_g_100g) %>%
  group_by(dish) %>%
  summarise(fat = fat_g_100g)
fat_dips
```

```{r}
fat_dips %>%
  ggplot() +
  aes(reorder(x = dish, fat), y = fat) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### saturated per 100g for dips

```{r}
sat_dips <- dips_100g %>%
  select(dish, sat_g_100g) %>%
  group_by(dish) %>%
  summarise(sat = sat_g_100g)
sat_dips
```

```{r}
sat_dips %>%
  ggplot() +
  aes(reorder(x = dish, sat), y = sat) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### carbs per 100g for dips

```{r}
carb_dips <- dips_100g %>%
  select(dish, carb_g_100g) %>%
  group_by(dish) %>%
  summarise(carbs = carb_g_100g)
carb_dips
```

```{r}
carb_dips %>%
  ggplot() +
  aes(reorder(x = dish, carbs), y = carbs) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### sugars per 100g for dips

```{r}
sugar_dips <- dips_100g %>%
  select(dish, sugars_g_100g) %>%
  group_by(dish) %>%
  summarise(sugar = sugars_g_100g)
sugar_dips
```

```{r}
sugar_dips %>%
  ggplot() +
  aes(reorder(x = dish, sugar), y = sugar) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### Fibre per 100g for dips

```{r}
fibre_dips <- dips_100g %>%
  select(dish, fibre_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = fibre_g_100g)
fibre_dips
```

```{r}
fibre_dips %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### Protein per 100g for dips

```{r}
protein_dips <- dips_100g %>%
  select(dish, protein_g_100g) %>%
  group_by(dish) %>%
  summarise(protein = protein_g_100g)
protein_dips
```


```{r}
protein_dips %>%
  ggplot() +
  aes(reorder(x = dish, protein), y = protein) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### Salt per 100g for dips

```{r}
salt_dips <- dips_100g %>%
  select(dish, salt_g_100g) %>%
  group_by(dish) %>%
  summarise(salt = salt_g_100g)
salt_dips
```

```{r}
salt_dips %>%
  ggplot() +
  aes(reorder(x = dish, salt), y = salt) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### sodium per 100g for dips

```{r}
sodium_dips <- dips_100g %>%
  select(dish, sodium_g_100g) %>%
  group_by(dish) %>%
  summarise(sodium = sodium_g_100g)
sodium_dips
```

```{r}
sodium_dips %>%
  ggplot() +
  aes(reorder(x = dish, sodium), y = sodium) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA for kcal for dips

```{r}
kcal_rda_dips <- dips_100g %>%
  select(dish, energy_kcal_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = energy_kcal_rda)
kcal_rda_dips
```

```{r}
kcal_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of fat for dips

```{r}
fat_rda_dips <- dips_100g %>%
  select(dish, fat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fat_rda)
fat_rda_dips
```

```{r}
fat_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of saturated for dips

```{r}
sat_rda_dips <- dips_100g %>%
  select(dish, sat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sat_rda)
sat_rda_dips
```

```{r}
sat_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of carbs for dips

```{r}
carb_rda_dips <- dips_100g %>%
  select(dish, carb_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = carb_rda)
carb_rda_dips
```

```{r}
carb_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of sugar for dips

```{r}
sugar_rda_dips <- dips_100g %>%
  select(dish, sugars_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sugars_rda)
sugar_rda_dips
```

```{r}
sugar_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of fibre for dips

```{r}
fibre_rda_dips <- dips_100g %>%
  select(dish, fibre_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fibre_rda)
fibre_rda_dips
```

```{r}
fibre_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of protein for dips


```{r}
protein_rda_dips <- dips_100g %>%
  select(dish, protein_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = protein_rda)
protein_rda_dips
```

```{r}
protein_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of salt for dips

```{r}
salt_rda_dips <- dips_100g %>%
  select(dish, salt_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = salt_rda)
salt_rda_dips
```

```{r}
salt_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```


### %RDA of sodium for dips

```{r}
sodium_rda_dips <- dips_100g %>%
  select(dish, sodium_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sodium_rda)
sodium_rda_dips
```

```{r}
sodium_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue")
```

