---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readxl)
library(janitor)
library(tidyverse)
```


```{r}
sides <- read_csv("clean_data/sides_clean.csv")
```


# Normalised macros for 100g are the same for some items that come in 2 portion sizes so one of them will be removed

```{r}
sides_100g <- sides %>%
  filter(type == "side") %>%
  filter(dish != "Chicken Kickers (14)" & dish != "Chicken Strippers (14)" &
           dish != "Chicken Wings (14)" & dish != "Pop'n Chicken Double Portion" &
           dish != "Potato Wedges IRL") 
```

```{r}
dips_100g <- sides %>%
  filter(type == "dip") %>%
  filter(dish != "BBQ Dip 100g" & dish != "Frank's Hot Dip 100g" &
           dish != "Garlic and Herb Dip 100g")
```



# SIDES

### kcal per 100g for sides

```{r}
kcal_sides <- sides_100g %>%
  select(dish, energy_kcal_100g) %>%
  group_by(dish) %>%
  summarise(energy_kcal = energy_kcal_100g)
kcal_sides
```


```{r}
kcal_sides %>%
  ggplot() +
  aes(reorder(x = dish, energy_kcal), y = energy_kcal) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Calories (kcal)") +
  ggtitle("Average amount of calories per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) 


```

### Fat per 100g for sides

```{r}
fat_sides <- sides_100g %>%
  select(dish, fat_g_100g) %>%
  group_by(dish) %>%
  summarise(fat = fat_g_100g)
fat_sides
```

```{r}
fat_sides %>%
  ggplot() +
  aes(reorder(x = dish, fat), y = fat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Fat (g)") +
  ggtitle("Average amount of fat per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### saturated per 100g for sides

```{r}
sat_sides <- sides_100g %>%
  select(dish, sat_g_100g) %>%
  group_by(dish) %>%
  summarise(sat = sat_g_100g)
sat_sides
```

```{r}
sat_sides %>%
  ggplot() +
  aes(reorder(x = dish, sat), y = sat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Saturated (g)") +
  ggtitle("Average amount of saturated per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### carbs per 100g of sides

```{r}
carb_sides <- sides_100g %>%
  select(dish, carb_g_100g) %>%
  group_by(dish) %>%
  summarise(carbs = carb_g_100g)
carb_sides
```


```{r}
carb_sides %>%
  ggplot() +
  aes(reorder(x = dish, carbs), y = carbs) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Carbs (g)") +
  ggtitle("Average amount of carbs per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### sugars per 100g for sides

```{r}
sugar_sides <- sides_100g %>%
  select(dish, sugars_g_100g) %>%
  group_by(dish) %>%
  summarise(sugar = sugars_g_100g)
sugar_sides
```

```{r}
sugar_sides %>%
  ggplot() +
  aes(reorder(x = dish, sugar), y = sugar) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Sugar (g)") +
  ggtitle("Average amount of sugar per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### fibre per 100g for sides

```{r}
fibre_sides <- sides_100g %>%
  select(dish, fibre_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = fibre_g_100g)
fibre_sides
```

```{r}
fibre_sides %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Fibre (g)") +
  ggtitle("Average amount of fibre per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### protein per 100g for sides

```{r}
protein_sides <- sides_100g %>%
  select(dish, protein_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = protein_g_100g)
protein_sides
```


```{r}
protein_sides %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Protein (g)") +
  ggtitle("Average amount of protein per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### salt per 100g for sides

```{r}
salt_sides <- sides_100g %>%
  select(dish, salt_g_100g) %>%
  group_by(dish) %>%
  summarise(salt = salt_g_100g)
salt_sides
```


```{r}
salt_sides %>%
  ggplot() +
  aes(reorder(x = dish, salt), y = salt) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Salt (g)") +
  ggtitle("Average amount of salt per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### sodium per 100g for sides

```{r}
sodium_sides <- sides_100g %>%
  select(dish, sodium_g_100g) %>%
  group_by(dish) %>%
  summarise(sodium = sodium_g_100g)
sodium_sides
```


```{r}
sodium_sides %>%
  ggplot() +
  aes(reorder(x = dish, sodium), y = sodium) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nAverage Sodium (g)") +
  ggtitle("Average amount of sodium per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```



### %RDA kcal for sides

```{r}
kcal_rda_sides <- sides_100g %>%
  select(dish, energy_kcal_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = energy_kcal_rda)
kcal_rda_sides
```


```{r}
kcal_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of calories per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA fat for sides

```{r}
fat_rda_sides <- sides_100g %>%
  select(dish, fat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fat_rda)
fat_rda_sides
```


```{r}
fat_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fat per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA saturated for sides

```{r}
sat_rda_sides <- sides_100g %>%
  select(dish, sat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sat_rda)
sat_rda_sides
```

```{r}
sat_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of saturated per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of carbs for sides

```{r}
carb_rda_sides <- sides_100g %>%
  select(dish, carb_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = carb_rda)
carb_rda_sides
```

```{r}
carb_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of carbs per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA sugars for sides

```{r}
sugar_rda_sides <- sides_100g %>%
  select(dish, sugars_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sugars_rda)
sugar_rda_sides
```

```{r}
sugar_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sugar per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA fibre of sides

```{r}
fibre_rda_sides <- sides_100g %>%
  select(dish, fibre_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fibre_rda)
fibre_rda_sides
```

```{r}
fibre_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fibre per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA protein for sides

```{r}
protein_rda_sides <- sides_100g %>%
  select(dish, protein_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = protein_rda)
protein_rda_sides
```


```{r}
protein_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of protein per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))

```


### %RDA salt for sides

```{r}
salt_rda_sides <- sides_100g %>%
  select(dish, salt_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = salt_rda)
salt_rda_sides
```


```{r}
salt_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of salt per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA sodium for sides

```{r}
sodium_rda_sides <- sides_100g %>%
  select(dish, sodium_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sodium_rda)
sodium_rda_sides
```


```{r}
sodium_rda_sides %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Side Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sodium per side type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


## Combined sides plots


### Fat and Sat RDAs

```{r}
fat_colours <- c("Fat" = "red", "Saturated" = "darkblue")

sides %>%
  filter(type == "side") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = sat_rda, col = "Fat"), group = 1) +
  geom_point(aes(y = sat_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= fat_rda, col = "Saturated"), group = 1) +
  geom_point(aes(y = fat_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = fat_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Fat and Saturated per side type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) 
```

### Carbs and Sugar RDAs

```{r}
carbs_colours <- c("Carbs" = "red", "Sugars" = "darkblue")

sides %>%
  filter(type == "side") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = carb_rda, col = "Carbs"), group = 1) +
  geom_point(aes(y = carb_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sugars_rda, col = "Sugars"), group = 1) +
  geom_point(aes(y = sugars_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = carbs_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Carbs and Sugar per side type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### Salt and Sodium RDAs

```{r}
salt_colours <- c("Salt" = "red", "Sodium" = "darkblue")

sides %>%
  filter(type == "side") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = salt_rda, col = "Salt"), group = 1) +
  geom_point(aes(y = salt_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sodium_rda, col = "Sodium"), group = 1) +
  geom_point(aes(y = sodium_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = salt_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Salt and Sodium per side type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```





# DIPS

### kcal per 100g for dips

```{r}
kcal_dips <- dips_100g %>%
  select(dish, energy_kcal_100g) %>%
  group_by(dish) %>%
  summarise(energy_kcal = energy_kcal_100g)
kcal_dips
```


```{r}
kcal_dips %>%
  ggplot() +
  aes(reorder(x = dish, energy_kcal), y = energy_kcal) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage calories (kcal)") +
  ggtitle("Average amount of calories per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### fat per 100g for dips

```{r}
fat_dips <- dips_100g %>%
  select(dish, fat_g_100g) %>%
  group_by(dish) %>%
  summarise(fat = fat_g_100g)
fat_dips
```

```{r}
fat_dips %>%
  ggplot() +
  aes(reorder(x = dish, fat), y = fat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage fat (g)") +
  ggtitle("Average amount of fat per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### saturated per 100g for dips

```{r}
sat_dips <- dips_100g %>%
  select(dish, sat_g_100g) %>%
  group_by(dish) %>%
  summarise(sat = sat_g_100g)
sat_dips
```

```{r}
sat_dips %>%
  ggplot() +
  aes(reorder(x = dish, sat), y = sat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage Saturated (g)") +
  ggtitle("Average amount of saturated per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### carbs per 100g for dips

```{r}
carb_dips <- dips_100g %>%
  select(dish, carb_g_100g) %>%
  group_by(dish) %>%
  summarise(carbs = carb_g_100g)
carb_dips
```

```{r}
carb_dips %>%
  ggplot() +
  aes(reorder(x = dish, carbs), y = carbs) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage Carbs (g)") +
  ggtitle("Average amount of carbs per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### sugars per 100g for dips

```{r}
sugar_dips <- dips_100g %>%
  select(dish, sugars_g_100g) %>%
  group_by(dish) %>%
  summarise(sugar = sugars_g_100g)
sugar_dips
```

```{r}
sugar_dips %>%
  ggplot() +
  aes(reorder(x = dish, sugar), y = sugar) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage Sugar (g)") +
  ggtitle("Average amount of Sugar per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### Fibre per 100g for dips

```{r}
fibre_dips <- dips_100g %>%
  select(dish, fibre_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = fibre_g_100g)
fibre_dips
```

```{r}
fibre_dips %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage Fibre (g)") +
  ggtitle("Average amount of fibre per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### Protein per 100g for dips

```{r}
protein_dips <- dips_100g %>%
  select(dish, protein_g_100g) %>%
  group_by(dish) %>%
  summarise(protein = protein_g_100g)
protein_dips
```


```{r}
protein_dips %>%
  ggplot() +
  aes(reorder(x = dish, protein), y = protein) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage Protein (g)") +
  ggtitle("Average amount of protein per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### Salt per 100g for dips

```{r}
salt_dips <- dips_100g %>%
  select(dish, salt_g_100g) %>%
  group_by(dish) %>%
  summarise(salt = salt_g_100g)
salt_dips
```

```{r}
salt_dips %>%
  ggplot() +
  aes(reorder(x = dish, salt), y = salt) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage Salt (g)") +
  ggtitle("Average amount of salt per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### sodium per 100g for dips

```{r}
sodium_dips <- dips_100g %>%
  select(dish, sodium_g_100g) %>%
  group_by(dish) %>%
  summarise(sodium = sodium_g_100g)
sodium_dips
```

```{r}
sodium_dips %>%
  ggplot() +
  aes(reorder(x = dish, sodium), y = sodium) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nAverage Sodium (g)") +
  ggtitle("Average amount of sodium per side type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA for kcal for dips

```{r}
kcal_rda_dips <- dips_100g %>%
  select(dish, energy_kcal_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = energy_kcal_rda)
kcal_rda_dips
```

```{r}
kcal_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of calories per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of fat for dips

```{r}
fat_rda_dips <- dips_100g %>%
  select(dish, fat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fat_rda)
fat_rda_dips
```

```{r}
fat_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fat per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of saturated for dips

```{r}
sat_rda_dips <- dips_100g %>%
  select(dish, sat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sat_rda)
sat_rda_dips
```

```{r}
sat_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of saturated per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of carbs for dips

```{r}
carb_rda_dips <- dips_100g %>%
  select(dish, carb_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = carb_rda)
carb_rda_dips
```

```{r}
carb_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of carbs per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of sugar for dips

```{r}
sugar_rda_dips <- dips_100g %>%
  select(dish, sugars_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sugars_rda)
sugar_rda_dips
```

```{r}
sugar_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sugar per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of fibre for dips

```{r}
fibre_rda_dips <- dips_100g %>%
  select(dish, fibre_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fibre_rda)
fibre_rda_dips
```

```{r}
fibre_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fibre per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of protein for dips


```{r}
protein_rda_dips <- dips_100g %>%
  select(dish, protein_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = protein_rda)
protein_rda_dips
```

```{r}
protein_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of protein per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of salt for dips

```{r}
salt_rda_dips <- dips_100g %>%
  select(dish, salt_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = salt_rda)
salt_rda_dips
```

```{r}
salt_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of salt per dip type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of sodium for dips

```{r}
sodium_rda_dips <- dips_100g %>%
  select(dish, sodium_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sodium_rda)
sodium_rda_dips
```

```{r}
sodium_rda_dips %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dip Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sodium per dips type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


## Combined plots for dips


### Fat and Sat

```{r}
fat_colours <- c("Fat" = "red", "Saturated" = "darkblue")

sides %>%
  filter(type == "dip") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = sat_rda, col = "Fat"), group = 1) +
  geom_point(aes(y = sat_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= fat_rda, col = "Saturated"), group = 1) +
  geom_point(aes(y = fat_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = fat_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Fat and Saturated per dip type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### Carbs and Sugar

```{r}
carbs_colours <- c("Carbs" = "red", "Sugars" = "darkblue")

sides %>%
  filter(type == "dip") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = carb_rda, col = "Carbs"), group = 1) +
  geom_point(aes(y = carb_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sugars_rda, col = "Sugars"), group = 1) +
  geom_point(aes(y = sugars_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = carbs_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Carbs and Sugars per dip type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### salt and sodium

```{r}
salt_colours <- c("Salt" = "red", "Sodium" = "darkblue")

sides %>%
  filter(type == "dip") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = salt_rda, col = "Salt"), group = 1) +
  geom_point(aes(y = salt_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sodium_rda, col = "Sodium"), group = 1) +
  geom_point(aes(y = sodium_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = salt_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Salt and Sodium per dip type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```



# Wrapzz

```{r}
wrapzz <- sides %>%
  filter(type == "wrapzz")
```


### kcal per 100g for wrapzz


```{r}
kcal_wrapzz <- wrapzz %>%
  select(dish, energy_kcal_100g) %>%
  group_by(dish) %>%
  summarise(kcal = energy_kcal_100g)
kcal_wrapzz
```


```{r}
kcal_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, kcal), y = kcal) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Calories (kcal)") +
  ggtitle("Average amount of calories per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### fat per 100g for wrapzz

```{r}
fat_wrapzz <- wrapzz %>%
  select(dish, fat_g_100g) %>%
  group_by(dish) %>%
  summarise(fat = fat_g_100g)
fat_wrapzz
```

```{r}
fat_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, fat), y = fat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Fat (g)") +
  ggtitle("Average amount of fat per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### saturated per 100g for wrapzz

```{r}
sat_wrapzz <- wrapzz %>%
  select(dish, sat_g_100g) %>%
  group_by(dish) %>%
  summarise(sat = sat_g_100g)
sat_wrapzz
```

```{r}
sat_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, sat), y = sat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Saturated (g)") +
  ggtitle("Average amount of saturated per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### carbs per 100g for wrapzz

```{r}
carb_wrapzz <- wrapzz %>%
  select(dish, carb_g_100g) %>%
  group_by(dish) %>%
  summarise(carbs = carb_g_100g)
carb_wrapzz
```

```{r}
carb_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, carbs), y = carbs) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Carbs (g)") +
  ggtitle("Average amount of carbs per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### sugars per 100g for wrapzz


```{r}
sugar_wrapzz <- wrapzz %>%
  select(dish, sugars_g_100g) %>%
  group_by(dish) %>%
  summarise(sugar = sugars_g_100g)
sugar_wrapzz
```

```{r}
sugar_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, sugar), y = sugar) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Sugar (g)") +
  ggtitle("Average amount of sugar per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### fibre per 100g for wrapzz

```{r}
fibre_wrapzz <- wrapzz %>%
  select(dish, fibre_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = fibre_g_100g)
fibre_wrapzz
```

```{r}
fibre_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Fibre (g)") +
  ggtitle("Average amount of fibre per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### protein per 100g for wrapzz

```{r}
protein_wrapzz <- wrapzz %>%
  select(dish, protein_g_100g) %>%
  group_by(dish) %>%
  summarise(protein = protein_g_100g)
protein_wrapzz
```

```{r}
protein_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, protein), y = protein) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Protein (g)") +
  ggtitle("Average amount of protein per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### salt per 100g for wrapzz

```{r}
salt_wrapzz <- wrapzz %>%
  select(dish, salt_g_100g) %>%
  group_by(dish) %>%
  summarise(salt = salt_g_100g)
salt_wrapzz
```

```{r}
salt_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, salt), y = salt) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Salt (g)") +
  ggtitle("Average amount of salt per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### sodium per 100g for wrapzz

```{r}
sodium_wrapzz <- wrapzz %>%
  select(dish, sodium_g_100g) %>%
  group_by(dish) %>%
  summarise(sodium = sodium_g_100g)
sodium_wrapzz
```

```{r}
sodium_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, sodium), y = sodium) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nAverage Sodium (g)") +
  ggtitle("Average amount of sodium per wrap type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA kcal for wrapzz

```{r}
kcal_rda_wrapzz <- wrapzz %>%
  select(dish, energy_kcal_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = energy_kcal_rda)
kcal_rda_wrapzz
```

```{r}
kcal_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of calories per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### %RDA fat for wrapzz

```{r}
fat_rda_wrapzz <- wrapzz %>%
  select(dish, fat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fat_rda)
fat_rda_wrapzz
```

```{r}
fat_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fat per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### %RDA of fat for wrapzz

```{r}
sat_rda_wrapzz <- wrapzz %>%
  select(dish, sat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sat_rda)
sat_rda_wrapzz
```

```{r}
sat_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of saturated per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA carbs for wrapzz

```{r}
carb_rda_wrapzz <- wrapzz %>%
  select(dish, carb_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = carb_rda)
carb_rda_wrapzz
```

```{r}
carb_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of carbs per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA sugar for wrapzz

```{r}
sugar_rda_wrapzz <- wrapzz %>%
  select(dish, sugars_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sugars_rda)
sugar_rda_wrapzz
```

```{r}
sugar_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sugar per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA fibre for wrapzz

```{r}
fibre_rda_wrapzz <- wrapzz %>%
  select(dish, fibre_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fibre_rda)
fibre_rda_wrapzz
```

```{r}
fibre_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fibre per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA of protein for wrapzz

```{r}
protein_rda_wrapzz <- wrapzz %>%
  select(dish, protein_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = protein_rda)
protein_rda_wrapzz
```

```{r}
protein_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of protein per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### %RDA salt for wrapzz

```{r}
salt_rda_wrapzz <- wrapzz %>%
  select(dish, salt_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = salt_rda)
salt_rda_wrapzz
```

```{r}
salt_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of salt per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA sodium for wrapzz


```{r}
sodium_rda_wrapzz <- wrapzz %>%
  select(dish, sodium_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sodium_rda)
sodium_rda_wrapzz
```

```{r}
sodium_rda_wrapzz %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Wrap Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sodium per wrap type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

## Combined plots

### Fat and Sat

```{r}
fat_colours <- c("Fat" = "red", "Saturated" = "darkblue")

sides %>%
  filter(type == "wrapzz") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = fat_rda, col = "Fat"), group = 1) +
  geom_point(aes(y = fat_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sat_rda, col = "Saturated"), group = 1) +
  geom_point(aes(y = sat_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = fat_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Fat and Saturated per Wrap type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### carbs and sugars

```{r}
carbs_colours <- c("Carbs" = "red", "Sugar" = "darkblue")

sides %>%
  filter(type == "wrapzz") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = carb_rda, col = "Carbs"), group = 1) +
  geom_point(aes(y = carb_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sugars_rda, col = "Sugar"), group = 1) +
  geom_point(aes(y = sugars_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = carbs_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Carbs and Sugar per Wrap type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### salt and sodium

```{r}
salt_colours <- c("Salt" = "red", "Sodium" = "darkblue")

sides %>%
  filter(type == "wrapzz") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = salt_rda, col = "Salt"), group = 1) +
  geom_point(aes(y = salt_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sodium_rda, col = "Sodium"), group = 1) +
  geom_point(aes(y = sodium_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = salt_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Salt and Sodium per Wrap type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```




# Desserts

```{r}
desserts <- sides %>%
  filter(type == "dessert")
```


### kcal per 100g for desserts

```{r}
kcal_desserts <- desserts %>%
  select(dish, energy_kcal_100g) %>%
  group_by(dish) %>%
  summarise(kcal = energy_kcal_100g)
kcal_desserts
```

```{r}
kcal_desserts %>%
  ggplot() +
  aes(reorder(x = dish, kcal), y = kcal) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Calories (kcal)") +
  ggtitle("Average amount of calories per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### fat per 100g for desserts


```{r}
fat_desserts <- desserts %>%
  select(dish, fat_g_100g) %>%
  group_by(dish) %>%
  summarise(fat = fat_g_100g)
fat_desserts
```

```{r}
fat_desserts %>%
  ggplot() +
  aes(reorder(x = dish, fat), y = fat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Fat (g)") +
  ggtitle("Average amount of fat per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### saturated per 100g for desserts

```{r}
sat_desserts <- desserts %>%
  select(dish, sat_g_100g) %>%
  group_by(dish) %>%
  summarise(sat = sat_g_100g)
sat_desserts
```

```{r}
sat_desserts %>%
  ggplot() +
  aes(reorder(x = dish, sat), y = sat) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Saturated (g)") +
  ggtitle("Average amount of saturated per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### carbs per 100g for desserts

```{r}
carb_desserts <- desserts %>%
  select(dish, carb_g_100g) %>%
  group_by(dish) %>%
  summarise(carb = carb_g_100g)
carb_desserts
```

```{r}
carb_desserts %>%
  ggplot() +
  aes(reorder(x = dish, carb), y = carb) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Carbs (g)") +
  ggtitle("Average amount of carbs per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### sugars per 100g for desserts

```{r}
sugar_desserts <- desserts %>%
  select(dish, sugars_g_100g) %>%
  group_by(dish) %>%
  summarise(sugar = sugars_g_100g)
sugar_desserts
```

```{r}
sugar_desserts %>%
  ggplot() +
  aes(reorder(x = dish, sugar), y = sugar) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Sugar (g)") +
  ggtitle("Average amount of sugar per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### fibre per 100g for desserts

```{r}
fibre_desserts <- desserts %>%
  select(dish, fibre_g_100g) %>%
  group_by(dish) %>%
  summarise(fibre = fibre_g_100g)
fibre_desserts
```

```{r}
fibre_desserts %>%
  ggplot() +
  aes(reorder(x = dish, fibre), y = fibre) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Fibre (g)") +
  ggtitle("Average amount of fibre per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### protein per 100g for desserts

```{r}
protein_desserts <- desserts %>%
  select(dish, protein_g_100g) %>%
  group_by(dish) %>%
  summarise(protein = protein_g_100g)
protein_desserts
```

```{r}
protein_desserts %>%
  ggplot() +
  aes(reorder(x = dish, protein), y = protein) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Protein (g)") +
  ggtitle("Average amount of protein per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### salt per 100g for desserts

```{r}
salt_desserts <- desserts %>%
  select(dish, salt_g_100g) %>%
  group_by(dish) %>%
  summarise(salt = salt_g_100g)
salt_desserts
```

```{r}
salt_desserts %>%
  ggplot() +
  aes(reorder(x = dish, salt), y = salt) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Salt (g)") +
  ggtitle("Average amount of salt per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### sodium per 100g for desserts

```{r}
sodium_desserts <- desserts %>%
  select(dish, sodium_g_100g) %>%
  group_by(dish) %>%
  summarise(sodium = sodium_g_100g)
sodium_desserts
```

```{r}
sodium_desserts %>%
  ggplot() +
  aes(reorder(x = dish, sodium), y = sodium) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nAverage Sodium (g)") +
  ggtitle("Average amount of sodium per dessert type (per 100g)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA kcal for desserts

```{r}
kcal_rda_desserts <- desserts %>%
  select(dish, energy_kcal_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = energy_kcal_rda)
kcal_rda_desserts
```

```{r}
kcal_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of calories per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA fat for desserts

```{r}
fat_rda_desserts <- desserts %>%
  select(dish, fat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fat_rda)
fat_rda_desserts
```

```{r}
fat_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fat per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA saturated for desserts

```{r}
sat_rda_desserts <- desserts %>%
  select(dish, sat_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sat_rda)
sat_rda_desserts
```

```{r}
sat_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of saturated per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA carbs for desserts


```{r}
carb_rda_desserts <- desserts %>%
  select(dish, carb_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = carb_rda)
carb_rda_desserts
```

```{r}
carb_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of carbs per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA sugar

```{r}
sugar_rda_desserts <- desserts %>%
  select(dish, sugars_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sugars_rda)
sugar_rda_desserts
```

```{r}
sugar_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sugar per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA fibre

```{r}
fibre_rda_desserts <- desserts %>%
  select(dish, fibre_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = fibre_rda)
fibre_rda_desserts
```

```{r}
fibre_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of fibre per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA protein for desserts

```{r}
protein_rda_desserts <- desserts %>%
  select(dish, protein_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = protein_rda)
protein_rda_desserts
```

```{r}
protein_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of protein per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA salt

```{r}
salt_rda_desserts <- desserts %>%
  select(dish, salt_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = salt_rda)
salt_rda_desserts
```

```{r}
salt_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of salt per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```


### %RDA sodium for desserts

```{r}
sodium_rda_desserts <- desserts %>%
  select(dish, sodium_rda) %>%
  group_by(dish) %>%
  summarise(percent_RDA = sodium_rda)
sodium_rda_desserts
```

```{r}
sodium_rda_desserts %>%
  ggplot() +
  aes(reorder(x = dish, percent_RDA), y = percent_RDA) +
  coord_flip() +
  geom_col(fill = "darkblue") +
  xlab("Dessert Type\n") +
  ylab("\nPercent RDA") +
  ggtitle("RDA of sodium per dessert type (percent)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

## combined plots

### fat and sat

```{r}
salt_colours <- c("Fat" = "red", "Saturated" = "darkblue")

sides %>%
  filter(type == "dessert") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = fat_rda, col = "Fat"), group = 1) +
  geom_point(aes(y = fat_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sat_rda, col = "Saturated"), group = 1) +
  geom_point(aes(y = sat_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = fat_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Fat and Saturated per dessert type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

### carbs and sugar

```{r}
carbs_colours <- c("Carbs" = "red", "Sugar" = "darkblue")

sides %>%
  filter(type == "dessert") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = carb_rda, col = "Carbs"), group = 1) +
  geom_point(aes(y = carb_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sugars_rda, col = "Sugar"), group = 1) +
  geom_point(aes(y = sugars_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = carbs_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Carb and Sugar per dessert type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

## salt and sodium

```{r}
salt_colours <- c("Salt" = "red", "Sodium" = "darkblue")

sides %>%
  filter(type == "dessert") %>%
  ggplot(aes(x = dish)) +
  geom_line(aes(y = salt_rda, col = "Salt"), group = 1) +
  geom_point(aes(y = salt_rda), col = "red", alpha = 0.7) +
  geom_line(aes(y= sodium_rda, col = "Sodium"), group = 1) +
  geom_point(aes(y = sodium_rda), col = "darkblue", alpha = 0.7) +
  labs(col = "Macro") +
  scale_colour_manual(values = salt_colours) +
  coord_flip() +
  xlab("Side Type\n") +
  ylab("\nRecommended Daily Allowance (%)") +
  ggtitle("RDA of Salt and Sodium per dessert type (per serving)\n") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14))
```

